---
title: "Summary of Project 3"
author: "Chengliang Tang"
date: "Nov 29, 2016"
output: pdf_document
---

## Feature extraction, storage, running time (cost)

### Submission Time
```{r, echo=FALSE}
# run Results.R first
submitTime <- c(550, 107, 28, 3, 63, 463, 7, 283, 48, 16, 113, 379)
submitTime_label <- c("2 Days Later", "5:02PM", "3:43PM", "3:18PM", "4:18PM", "10:58PM", "3:22PM", "7:58PM", "4:03PM", "3:31PM", "5:08PM", "9:34PM")

bar_time <- barplot(submitTime, main="Submission Time: Minutues from 3:15PM",
        xlab="Team", ylab="Minutes", ylim=c(0, 650))
text(bar_time, submitTime+50, submitTime_label, cex=0.7)
axis(1, bar_time, labels=as.character(1:12))
```

### Dimensions of Extracted Features
#### Advanced Model
```{r, echo=FALSE}
featureDim_bl <- c(6280, 500, NA, 800, 6000, 6000, 512, 196, 43266, 5033, 2141, 1200)
log_featureDim_bl <- log(featureDim_bl)
bar_dim_bl <- barplot(log_featureDim_bl, main="Extracted Advanced Feature Dimensions",
                       xlab="Team", ylab="log(p)", ylim=c(0, 15))
text(bar_dim_bl, log_featureDim_bl+2, as.character(featureDim_bl), cex=0.8)
axis(1, bar_time, labels=as.character(1:12))
```

### Running Time
```{r, echo=FALSE}
# run Results.R first
RunningTime <- c(10.98, 4.41, NA, 1.01, 6.57, 3.14, 24, 1.45, 60.15, 1.86, 5, 0.01)
bar_time <- barplot(RunningTime, main="Running Time",
        xlab="Team", ylab="Minutes", ylim=c(0, 70))
text(bar_time, RunningTime+5, as.character(RunningTime), cex=0.7)
axis(1, bar_time, labels=as.character(1:12))
```

## Performance
### Baseline Prediction Accuracy

```{r, echo=FALSE}
# data saved in Results.R
err_claimed <- c(0.34, 0.294, 0.326, 0.348, 0.3115, 0.33, 0.2975, 0.284, 0.29, 0.25, 0.28, 0.287)
err_adv_claimed <- rep(err_claimed, each=20)
CV_error_baseline <- c(
  0.1775, 0.1750, 0.1705, 0.1685, 0.1660,
  0.480, 0.461, 0.475, 0.444, 0.443,
  0.32, 0.39, 0.333, 0.31, 0.262,
  0.3260, 0.3150, 0.3250, 0.3255, 0.3200,
  0.0935, 0.0920, 0.0915, 0.0905, 0.0920,
  0.3400, 0.3825, 0.3625, 0.3350, 0.3050,
  0.3600, 0.3850, 0.3825, 0.3625, 0.3475,
  0.2850, 0.3025, 0.2950, 0.3150, 0.2900,
  0.545, 0.5625, 0.5675, 0.605, 0.6225,
  0.4250, 0.3775, 0.4100, 0.3650, 0.4100,
  0.2900, 0.3100, 0.2800, 0.2575, 0.2525,
  0.3000, 0.2925, 0.2900, 0.3025, 0.2700
)
# load("label_eval.RData")
# load("pred_untuned.RData")
# ind_fun <- which(is.na(label_eval))
err_untuned <- c(0.2035, 0.296, 0.34, 0.321, 0.0815, 0.355, 0.258, 0.281, 0.5435, 0.2425, 0.266, 0.2385)
err_adv_untuned <- rep(err_untuned  , each=20)

type_names <- c("claimed", "untuned", "re-trained")
# team_names <- paste0("Team ", 1:12)
team_names <- 1:12
# load("output_proj3.RData")
err_adv_all <- data.frame(Team=rep(rep(team_names, each=20), times=3), 
  					  Type=rep(type_names, each=240),
						  Error= c(err_adv_claimed, err_adv_untuned, rep(CV_error_baseline, each = 4))) #as.vector(t(output$err_adv_retrained))))

err_adv_all$Type <- factor(err_adv_all$Type, levels= type_names)
err_adv_all$Team <- factor(err_adv_all$Team, levels= team_names)


err_adv_all$Error <- err_adv_all$Error*100

type_names <- c("claimed", "untuned", "re-trained")
team_names <- paste0("Team ", 1:12)

library(ggplot2)
(ggplot(err_adv_all, aes(y = Error, x = Team, fill = Type, colour = Type)) 
+ geom_boxplot(width=0.5,outlier.colour = NULL)
#+ scale_alpha_continuous(guide=FALSE, range=c(0.01,0.99))
+theme(axis.line = element_line(colour = "black"),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_rect(colour = "black", fill=NA),
      axis.text=element_text(size=12),
      axis.title=element_text(size=12),
      legend.text=element_text(size=12),
      legend.title=element_text(size=12, face="bold"),
      legend.position="bottom",
      strip.text.y = element_text(size = 13, face="bold"),
      panel.background = element_blank())
+ labs(title="Baseline Model CV Error (%)", x="Team", y="Error Rate")
+ scale_colour_brewer(palette = "Dark2", guide = FALSE)
+ scale_fill_brewer(palette = "Pastel2", labels=type_names, guide = guide_legend(title = "Type"))
+ geom_vline(xintercept = seq(1.5, 12.5, 1), linetype = "longdash", colour="lightgrey")) 

```

### Advanced Prediction Accuracy
Advanced models: SVM(1, 2, 4, 9), CNN(3), xgboost(5), gbm(6, 11), majority vote(7, 10), random forest(8), logistic(12)

```{r, echo=FALSE}
err_claimed <- c(0.198, 0.13, 0.078, 0.122, 0.079, 0.089, 0.0875, 0.1295, 0.0907, 0.18, 0.20, 0.15)
err_adv_claimed <- rep(err_claimed, each=20)
CV_error_adv <- c(
  0.2030, 0.1925, 0.2060, 0.1950, 0.1985,
  0.1610, 0.1635, 0.1565, 0.1565, 0.1405,
  0.0775, 0.0625, 0.085, 0.0737, 0.0813,
  0.1260, 0.1210, 0.1325, 0.1225, 0.1260,
  0.0795, 0.0805, 0.0785, 0.0825, 0.0885,
  0.0925, 0.1175, 0.0825, 0.0900, 0.0850,
  0.075, 0.1075, 0.0725, 0.06, 0.065,
  0.1200, 0.1225, 0.1400, 0.1575, 0.1350,
  0.3125, 0.65, 0.25, 0.62, 0.675,
  0.2150, 0.2200, 0.2150, 0.1675, 0.2050,
  0.1300, 0.1000, 0.1050, 0.1425, 0.1050,
  0.0775, 0.0725, 0.0500, 0.0675, 0.0800
)
#load("label_eval.RData")
#load("pred_untuned.RData")
# ind_fun <- which(is.na(label_eval))
err_untuned <- c(0.2445, 0.137, 0.066, 0.106, 0.0665, 0.0805, 0.0645, 0.1365, 0.202, 0.1695, 0.136, 0.066)
err_adv_untuned <- rep(err_untuned  , each=20)

type_names <- c("claimed", "untuned", "re-trained")
# team_names <- paste0("Team ", 1:12)
team_names <- 1:12
# load("output_proj3.RData")
err_adv_all <- data.frame(Team=rep(rep(team_names, each=20), times=3), 
  					  Type=rep(type_names, each=240),
						  Error= c(err_adv_claimed, err_adv_untuned, rep(CV_error_adv, each = 4))) #as.vector(t(output$err_adv_retrained))))

err_adv_all$Type <- factor(err_adv_all$Type, levels= type_names)
err_adv_all$Team <- factor(err_adv_all$Team, levels= team_names)


err_adv_all$Error <- err_adv_all$Error*100

type_names <- c("claimed", "untuned", "re-trained")
team_names <- paste0("Team ", 1:12)

library(ggplot2)
(ggplot(err_adv_all, aes(y = Error, x = Team, fill = Type, colour = Type)) 
+ geom_boxplot(width=0.5,outlier.colour = NULL)
#+ scale_alpha_continuous(guide=FALSE, range=c(0.01,0.99))
+theme(axis.line = element_line(colour = "black"),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_rect(colour = "black", fill=NA),
      axis.text=element_text(size=12),
      axis.title=element_text(size=12),
      legend.text=element_text(size=12),
      legend.title=element_text(size=12, face="bold"),
      legend.position="bottom",
      strip.text.y = element_text(size = 13, face="bold"),
      panel.background = element_blank())
+ labs(title="Advanced Model CV Error (%)", x="Team", y="Error Rate")
+ scale_colour_brewer(palette = "Dark2", guide = FALSE)
+ scale_fill_brewer(palette = "Pastel2", labels=type_names, guide = guide_legend(title = "Type"))
+ geom_vline(xintercept = seq(1.5, 12.5, 1), linetype = "longdash", colour="lightgrey")) 

```



## Fun Images

The prediction of 20 fun images. 

```{r, echo=FALSE}
library(EBImage)
resetPar <- function() {
	dev.new()
  op <- par(no.readonly = TRUE)
	dev.off()
  op
}
ind_1 <- c("0273", "0274", "0328", "0492", "0532", "0576", "0599", "0609", "0834", "0839", "0862", "0974", "1089", "1093", "1268", "1387", "1389", "1517", "1757", "1803")
ind_2 <- c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10", "11", "12", "13", "14","15", "16", "17", "18", "19", "20")
for (i in 1:20){
  img_1 <- readImage(paste0("image_", ind_1[i],".jpg")) 
  display(img_1)
  #text(x = 20, y = 20, label = paste0("img_", ind_1[i], ".jpg"), adj = c(0,1), col = "red", cex = 2)
  par(resetPar())
	par(mar=c(7,4,4,2))
  img_2 <- readImage(paste0("Rplot_", ind_2[i],".jpeg")) 
  display(img_2)
}

```

## Summary of Common Problems
* Ease of Reproducibility(train.R & test.R): Input and Output
* Abosolute path: setwd("F:/UNI/ADS_2016/project3/output")
  Relative path: setwd("~/output")
  
  
  
  
  
  
  
  
  
  
  
  
  
  
 

