---
title: "Lyrics ShinyApp"
author: "Chengliang Tang, Arpita Shah, Yujie Wang and Tian Zheng"
output: html_notebook
runtime: shiny
---

"lyrics_filter.csv" is a filtered corpus of 380,000+ song lyrics from from MetroLyrics. You can read more about it on [Kaggle](https://www.kaggle.com/gyani95/380000-lyrics-from-metrolyrics).

"info_artist.csv" provides the background information of all the artistis. These information are scraped from [LyricsFreak](https://www.lyricsfreak.com/).

Here, we explore these data sets and try to find interesting patterns.

### Load all the required libraries

From the packages' descriptions:

+ `tidyverse` is an opinionated collection of R packages designed for data science. All packages share an underlying design philosophy, grammar, and data structures;
+ `tidytext` allows text mining using 'dplyr', 'ggplot2', and other tidy tools;
+ `plotly` allows plotting interactive graphs;
+ `DT` provides an R interface to the JavaScript library DataTables;
+ `tm` is a framework for text mining applications within R;
+ `scales` map data to aesthetics, and provide methods for automatically determining breaks and labels for axes and legends;
+ `data.table` is a package for fast aggregation of large data;
+ `wordcloud2` provides an HTML5 interface to wordcloud for data visualization;
+ `gridExtra` contains miscellaneous functions for "grid" graphics;
+ `ngram` is for constructing n-grams (“tokenizing”), as well as generating new text based on the n-gram structure of a given text input (“babbling”);
+ `Shiny` is an R package that makes it easy to build interactive web apps straight from R;

```{r load libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(tidytext)
library(plotly)
library(DT)
library(tm)
library(data.table)
library(scales)
library(wordcloud2)
library(gridExtra)
library(ngram)
library(shiny) 
```


### Load the processed lyrics data along with artist information

We use the processed data and artist information for our analysis.

```{r load data, warning=FALSE, message=FALSE}
# load lyrics data
load('../output/processed_lyrics.RData') 
# load artist information
dt_artist <- fread('../data/artists.csv') 
```

### Preparations for visualization
```{r}
lyrics_list <- c("Folk", "R&B", "Electronic", "Jazz", "Indie", "Country", "Rock", "Metal", "Pop", "Hip-Hop", "Other")
time_list <- c("1970s", "1980s", "1990s", "2000s", "2010s")
corpus <- VCorpus(VectorSource(dt_lyrics$stemmedwords))
word_tibble <- tidy(corpus) %>%
  select(text) %>%
  mutate(id = row_number()) %>%
  unnest_tokens(word, text)
```



### Specify the user interface for the R Shiny app
```{r}
# Define UI for app that draws a histogram ----
ui <- navbarPage(strong("Lyrics Analysis"),
  tabPanel("Overview",
    titlePanel("Most frequent words"),
    # Sidebar layout with input and output definitions ----
    sidebarLayout(
      # Sidebar panel for inputs ----
      sidebarPanel(
        sliderInput(inputId = "nwords1",
                    label = "Number of terms in the first word cloud:",
                    min = 5, max = 100, value = 50),
        selectInput('genre1', 'Genre of the first word cloud', 
                    lyrics_list, selected='Folk')

    ),
    # Main panel for displaying outputs ----
    mainPanel(
      wordcloud2Output(outputId = "WC1", height = "300")
    )
  ),
  hr(),
  sidebarLayout(
      # Sidebar panel for inputs ----
      sidebarPanel(
        sliderInput(inputId = "nwords2",
                    label = "Number of terms in the second word cloud:",
                    min = 5, max = 100, value = 50),
        selectInput('genre2', 'Genre of the second word cloud', 
                    lyrics_list, selected='Metal')
    ),
    # Main panel for displaying outputs ----
    mainPanel(
      wordcloud2Output(outputId = "WC2", height = "300")
    )
  )
           ),
  tabPanel("Time Variation",
           # Sidebar layout with input and output definitions ----
          sidebarLayout(
            # Sidebar panel for inputs ----
            sidebarPanel(
              selectInput('decade1', 'Selected decade for the first plot:', 
                          time_list, selected='1970s'),
              selectInput('decade2', 'Selected decade for the second plot:', 
                          time_list, selected='1980s'),
              numericInput(inputId = "topBigrams",
                                          label = "Number of top pairs to view:",
                                          min = 1,
                                          max = 20,
                                          value = 10)
      
          ),
          # Main panel for displaying outputs ----
          mainPanel(
            fluidRow(
              column(5,
                     plotlyOutput("bigram1")),
              column(5,
                     plotlyOutput("bigram2"))
            )
          )
        )
           ),
  tabPanel("Data", 
           DT::dataTableOutput("table"))
)
```


### Develop the server for the R Shiny app
This shiny app visualizes summary of data and displays the data table itself.

# Define server logic required for ui ----
```{r}
server <- function(input, output) {
  output$WC1 <- renderWordcloud2({
    count(filter(word_tibble, id %in% which(dt_lyrics$genre == input$genre1)), word, sort = TRUE) %>%
      slice(1:input$nwords1) %>%
      wordcloud2(size=0.6, rotateRatio=0.2)
  })
  output$WC2 <- renderWordcloud2({
    count(filter(word_tibble, id %in% which(dt_lyrics$genre == input$genre2)), word, sort = TRUE) %>%
      slice(1:input$nwords2) %>%
      wordcloud2(size=0.6, rotateRatio=0.2)
  })
  output$bigram1 <- renderPlotly({
    year_start <- as.integer(substr(input$decade1, 1, 4))
    dt_sub <- filter(dt_lyrics, year>=year_start) %>%
      filter(year<(year_start+10))
    lyric_bigrams <- dt_sub %>%
      unnest_tokens(bigram, stemmedwords, token = "ngrams", n = 2)
    bigram_counts <- lyric_bigrams %>%
      separate(bigram, c("word1", "word2"), sep = " ") %>%
      count(word1, word2, sort = TRUE)
    combined_words <- apply(bigram_counts[c(1, 2)], 1, paste , collapse = " " )[1:input$topBigrams]
    x_names <- factor(combined_words, levels = rev(combined_words))
    plot_ly(
      x = bigram_counts$n[1:input$topBigrams],
      y = x_names,
      name = "Bigram",
      type = "bar",
      orientation = 'h'
    )
  })
  output$bigram2 <- renderPlotly({
    year_start <- as.integer(substr(input$decade2, 1, 4))
    dt_sub <- filter(dt_lyrics, year>=year_start) %>%
      filter(year<(year_start+10))
    lyric_bigrams <- dt_sub %>%
      unnest_tokens(bigram, stemmedwords, token = "ngrams", n = 2)
    bigram_counts <- lyric_bigrams %>%
      separate(bigram, c("word1", "word2"), sep = " ") %>%
      count(word1, word2, sort = TRUE)
    combined_words <- apply(bigram_counts[c(1, 2)], 1, paste , collapse = " " )[1:input$topBigrams]
    x_names <- factor(combined_words, levels = rev(combined_words))
    plot_ly(
      x = bigram_counts$n[1:input$topBigrams],
      y = x_names,
      name = "Bigram",
      type = "bar",
      orientation = 'h'
    )
  })
  output$table <- DT::renderDataTable({
    DT::datatable(dt_lyrics)
  })
}
```

### Run the R Shiny app

```{r shiny app, warning=FALSE, message=FALSE}
shinyApp(ui, server)
```





