---
title: "Summary of Project 3"
author: "Chengliang Tang"
date: "November 29, 2017"
output:
  html_document: default
  pdf_document: default
---

## Feature extraction, storage, running time (cost)

### Submission Time
```{r, echo=FALSE}
# run Results.R first
submitTime <- c(0, 1, 0, 127, 250, 131, 10, 7, 182)
submitTime_label <- c("In Time", "6:51PM", "In Time", "8:57PM", "One day later", "9:01PM", "7:00PM", "6:57PM", "9:52PM")

bar_time <- barplot(submitTime, main="Submission Time: Minutues from 6:50 PM",
        xlab="Team", ylab="Minutes", ylim=c(0, 300))
text(bar_time, submitTime+30, submitTime_label, cex=0.6)
axis(1, bar_time, labels=as.character(1:9))
```

### Dimensions of Extracted Features
#### Advanced Model
Advanced Features: GIST(5), resized SIFT(2, 3, 9), CNN(1), LBP(3, 4, 6, 9), HoG(3, 8), color(3, 7)
```{r, echo=FALSE}
featureDim_bl <- c(3, 100, 5763, 555, 960, 59, 1440, 54, 7277)
log_featureDim_bl <- log(featureDim_bl)
bar_dim_bl <- barplot(log_featureDim_bl, main="Extracted Advanced Feature Dimensions",
                       xlab="Team", ylab="log(p)", ylim=c(0, 12))
text(bar_dim_bl, log_featureDim_bl+0.5, as.character(featureDim_bl), cex=0.8)
axis(1, bar_time, labels=as.character(1:9))
```

### Running Time
Advanced models: SVM(6), xgboost(2, 3, 5, 7), majority vote(8), CNN(1), logistic regression(4), AdaBoost(9)
```{r, echo=FALSE}
# run Results.R first
RunningTime <- c(9240.48, 378.89, 194.66, 9.443626, 30.4, 1.5, 24.26, 6.7, 1800.6)
log_RunningTime <- log(RunningTime)
bar_time <- barplot(log_RunningTime, main="Advanced Model Running Time",
        xlab="Team", ylab="log(t)", ylim=c(0, 10))
text(bar_time, log_RunningTime+0.5, as.character(RunningTime), cex=0.8)
axis(1, bar_time, labels=as.character(1:9))
```

## Performance
### Baseline Prediction Accuracy

```{r, echo=FALSE}
# data saved in Results.R
err_claimed <- c(0.2067, 0.297, 0.2, 0.25, 0.2227, 0.269, 0.19, 0.234, 0.204)
err_adv_claimed <- rep(err_claimed, each=20)
CV_error_baseline <- c(
  0.217,
0.283,
0.208,
0.22,
0.276,
0.281,
0.193,
0.235,
0.218)
err_retrained <- rep(CV_error_baseline, each=20)
# load("label_eval.RData")
# load("pred_untuned.RData")
# ind_fun <- which(is.na(label_eval))
err_untuned <- c(0.228,
0.449,
0.217,
0.168,
0.237,
0.281,
0.201,
0.269,
0.265)
err_adv_untuned <- rep(err_untuned  , each=20)

type_names <- c("claimed", "untuned", "re-trained")
# team_names <- paste0("Team ", 1:12)
team_names <- 1:9
# load("output_proj3.RData")
err_adv_all <- data.frame(Team=rep(rep(team_names, each=20), times=3), 
  					  Type=rep(type_names, each=180),
						  Error= c(err_adv_claimed, err_adv_untuned, err_retrained)) #as.vector(t(output$err_adv_retrained))))

err_adv_all$Type <- factor(err_adv_all$Type, levels= type_names)
err_adv_all$Team <- factor(err_adv_all$Team, levels= team_names)


err_adv_all$Error <- err_adv_all$Error*100

type_names <- c("claimed", "untuned", "re-trained")
team_names <- paste0("Team ", 1:9)

library(ggplot2)
(ggplot(err_adv_all, aes(y = Error, x = Team, fill = Type, colour = Type)) 
+ geom_boxplot(width=0.5,outlier.colour = NULL)
#+ scale_alpha_continuous(guide=FALSE, range=c(0.01,0.99))
+theme(axis.line = element_line(colour = "black"),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_rect(colour = "black", fill=NA),
      axis.text=element_text(size=12),
      axis.title=element_text(size=12),
      legend.text=element_text(size=12),
      legend.title=element_text(size=12, face="bold"),
      legend.position="bottom",
      strip.text.y = element_text(size = 13, face="bold"),
      panel.background = element_blank())
+ labs(title="Baseline Model CV Error (%)", x="Team", y="Error Rate")
+ scale_colour_brewer(palette = "Dark2", guide = FALSE)
+ scale_fill_brewer(palette = "Pastel2", labels=type_names, guide = guide_legend(title = "Type"))
+ geom_vline(xintercept = seq(1.5, 13.5, 1), linetype = "longdash", colour="lightgrey")) 

```

### Advanced Prediction Accuracy
Advanced Features: GIST(5), resized SIFT(2, 3, 9), CNN(1), LBP(3, 4, 6, 9), HoG(3, 8), color(3, 7)

Advanced models: SVM(6), xgboost(2, 3, 5, 7), majority vote(8), CNN(1), logistic regression(4), AdaBoost(9)

```{r, echo=FALSE}
# data saved in Results.R
err_claimed <- c(0.062,
0.1733,
0.11,
0.18,
0.1328,
0.1957,
0.093,
0.169,
0.085)
err_adv_claimed <- rep(err_claimed, each=20)
CV_error_baseline <- c(
0.0733,
0.1878,
0.1283,
0.1633,
0.126,
0.219,
0.096,
0.271,
0.105)
err_retrained <- rep(CV_error_baseline, each=20)
# load("label_eval.RData")
# load("pred_untuned.RData")
# ind_fun <- which(is.na(label_eval))
err_untuned <- c(0.233,
0.337,
0.257,
0.166,
0.15,
0.24,
0.093,
0.427,
0.403)
err_adv_untuned <- rep(err_untuned  , each=20)

type_names <- c("claimed", "untuned", "re-trained")
# team_names <- paste0("Team ", 1:12)
team_names <- 1:9
# load("output_proj3.RData")
err_adv_all <- data.frame(Team=rep(rep(team_names, each=20), times=3), 
  					  Type=rep(type_names, each=180),
						  Error= c(err_adv_claimed, err_adv_untuned, err_retrained)) #as.vector(t(output$err_adv_retrained))))

err_adv_all$Type <- factor(err_adv_all$Type, levels= type_names)
err_adv_all$Team <- factor(err_adv_all$Team, levels= team_names)


err_adv_all$Error <- err_adv_all$Error*100

type_names <- c("claimed", "untuned", "re-trained")
team_names <- paste0("Team ", 1:9)

library(ggplot2)
(ggplot(err_adv_all, aes(y = Error, x = Team, fill = Type, colour = Type)) 
+ geom_boxplot(width=0.5,outlier.colour = NULL)
#+ scale_alpha_continuous(guide=FALSE, range=c(0.01,0.99))
+theme(axis.line = element_line(colour = "black"),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_rect(colour = "black", fill=NA),
      axis.text=element_text(size=12),
      axis.title=element_text(size=12),
      legend.text=element_text(size=12),
      legend.title=element_text(size=12, face="bold"),
      legend.position="bottom",
      strip.text.y = element_text(size = 13, face="bold"),
      panel.background = element_blank())
+ labs(title="Advanced Model CV Error (%)", x="Team", y="Error Rate")
+ scale_colour_brewer(palette = "Dark2", guide = FALSE)
+ scale_fill_brewer(palette = "Pastel2", labels=type_names, guide = guide_legend(title = "Type"))
+ geom_vline(xintercept = seq(1.5, 13.5, 1), linetype = "longdash", colour="lightgrey")) 
```



  
  
  
  
  
  
  
  
  
  
  
 

