---
title: "Sample ACS Analysis: Should I do a PhD?"
author: "Yuting Ma, Ke Shen"
date: "January 25, 2016"
output: html_document
---

#Introduction
This is a sample ACS analysis from Kaggle script <https://www.kaggle.com/owise83/d/census/2013-american-community-survey/should-i-do-a-phd/code>.

The goal of this analysis is to empirically check if an US citizen/resident should pursue his/her education to higher levels, whether it is worth doing it, and if so where abouts (which states), is there a correlation or pattern between higher income and higher degree level? 

The aim is not to end up being a PhD holder looking for a job or being less paid than MSc or B.Sc. To answer these questions, the author concentrated on B.Sc, MSc, and PhD holders, their personal income, their employment status, and their whereabouts. 

##Setup the libraries
Libraries we need along the way
```{r, message = F}
library("dplyr")
library("data.table")
library("ggplot2")
library("choroplethr")
```

##Read the data
```{r}
load("./data/populData.RData")
```
##Data Manipulation
Convert it to `tbl_df` for easier manipulation: remove `NAs`, extract BSc, MSc, and PhD, and group them accordingly:
```{r}
populData <- tbl_df(populData) 
ds <-  populData %>%  
  na.omit() %>%
  filter(SCHL %in%  c(21,22,24)) %>%
  group_by(SCHL) 
rm(populData)
```

Map the codes of the school level to the proper names of the degrees
```{r, echo=FALSE}
degreeCode = "SCHL,DegLevel
21,Bachelor 
22,Masters
24,Doctorate"
degreCodes <- fread(degreeCode)  
```

##How many are they?
First we want to see and to compare the number of BSc , MSc, and PhD holders all over the states.

```{r, echo=FALSE}
#Visualization
degreeHolders <-  summarise(ds, count=n())
degreeHolders <- left_join(degreeHolders , degreCodes, by.x=c("SCHL"))
Degrees <- factor(degreeHolders$DegLevel, levels = unique(degreeHolders$DegLevel))

ggplot(degreeHolders, aes(x= Degrees , y=degreeHolders$count, fill= Degrees)) +                        
  geom_bar(stat="identity") + scale_fill_hue(l=40) +
  ylab("No of People") + 
  xlab("Degree") + ggtitle("Comparing Degrees Holders in the US") +
  theme(axis.text.x = element_text(angle = 30, hjust = 1),
        panel.background = element_rect(fill = 'white' ))
```

We can see BSc holders are much more than the MSc and PhD degrees.
OK, now we got an idea how many BSc, MSc, and PhD degrees in the states, so let us now compare their unemployment rates: 
  
```{r}
#Filter unemployed, group them by degree and calculate rates:
jobLess <- ds %>%
  filter(ESR==3)%>% #3 indicates  Unemployed
  group_by(SCHL) %>% 
  summarise(count=n())%>%
  mutate(Percet = count/degreeHolders$count*100)
```           


```{r, echo=FALSE}
ggplot(jobLess, aes(x= Degrees , y=jobLess$Percet, fill= Degrees)) +                        
  geom_bar(stat="identity") + scale_fill_hue(l=80) +
  ylab("Percent %") + 
  xlab("Degree") + ggtitle("Percentages of Unemployed Degree  Holders")+
  theme(axis.text.x = element_text(angle = 30, hjust = 1),
        panel.background = element_rect(fill = 'white' ))
```

It is clear that PhD degrees have the lowest unemployment rate, and it is unlikely that you will be jobless if you do a PhD specifically in particular states. 

#Which states are these?
We are interested in which states have the highest unemployment rate for each group of degree levels. To start with, I  do state code mapping here, write it into a data frame and then  bind  it with `jobLessBSc` extracted below

```{r, echo=FALSE}
stateCodeCSV = "ST,region
001,alabama
002,alaska
004,arizona
005,arkansas
006,california
008,colorado
009,connecticut
010,delaware
011,district of columbia
012,florida
013,georgia
015,hawaii
016,idaho
017,illinois
018,indiana
019,iowa
020,kansas
021,kentucky
022,louisiana
023,maine
024,maryland
025,massachusetts
026,michigan
027,minnesota
028,mississippi
029,missouri
030,montana
031,nebraska
032,nevada
033,new hampshire
034,new jersey
035,new mexico
036,new york
037,north carolina
038,north dakota
039,ohio
040,oklahoma
041,oregon
042,pennsylvania
044,rhode island
045,south carolina
046,south dakota
047,tennessee
048,texas
049,utah
050,vermont
051,virginia
053,washington
054,west virginia
055,wisconsin
056,wyoming"
stateCodes <- fread(stateCodeCSV)
```

Then find the total number of B.Sc holders in each state, count   those who are unemployed,  then  compute thier precntages in each state, and finally visualize where they live: 
  
```{r, message =FALSE}
stateTotalBSc  <- ds%>%
  filter(SCHL==21)%>%
  group_by(ST)%>%
  summarise(count = n())

#Do the join before percentage computation to make sure you have a count for each state including 0s
jobLessBSc  <- ds%>%
  filter(SCHL==21, ESR==3)%>%
  group_by(ST)%>%
  summarise(count = n())

jobLessBSc <- right_join(jobLessBSc , stateCodes, by.x=c("ST"))
jobLessBSc[is.na(jobLessBSc)] <- 0
jobLessBSc <- mutate(jobLessBSc, value = jobLessBSc$count/stateTotalBSc$count*100)

```


which produces the this:
```{r, echo=FALSE}
state_choropleth(jobLessBSc, title = "Percentage of Unemployed BSc Holders", num_colors=9)
```

Do the same with MSc:
```{r, echo=FALSE, message =FALSE}
stateTotalMSc  <- ds%>%
  filter(SCHL==22)%>%
  group_by(ST)%>%
  summarise(count = n())

jobLessMSc  <- ds%>%
  filter(SCHL==22, ESR==3)%>%
  group_by(ST)%>%
  summarise(count = n())

#Do the join before percentage computation to make sure you have a count for each state including 0s
jobLessMSc <- right_join(jobLessMSc , stateCodes, by.x=c("ST"))
jobLessMSc[is.na(jobLessMSc)] <- 0
jobLessMSc <- mutate(jobLessMSc, value = jobLessMSc$count/stateTotalMSc$count*100)

#Plot Map
state_choropleth(jobLessMSc, title = "Percentage of Unemployed MSc Holders", num_colors=9)
```

and PhD guys:
```{r, echo=FALSE, message =FALSE}
stateTotalPhD  <- ds%>%
  filter(SCHL==24)%>%
  group_by(ST)%>%
  summarise(count = n())

jobLessPhD <- ds%>%
  filter(SCHL==24, ESR==3)%>%
  group_by(ST)%>%
  summarise(count = n())

#Do the join before percentage computation to make sure you have a count for each state including 0s
jobLessPhD <- right_join(jobLessPhD , stateCodes, by.x=c("ST"))
jobLessPhD[is.na(jobLessPhD)] <- 0
jobLessPhD <- mutate(jobLessPhD, value = jobLessPhD$count/stateTotalPhD$count*100)

#Plot Map
state_choropleth(jobLessPhD, title = "Percentage of Unemployed PhD Holders", num_colors=9)
```

# Top 10 States Analysis
Let us now see which top 10 states have the highest unemployment rate, and which ones have the lowest unemployment rate  for each degree group: 

### BSc
```{r}
#Find which states have  the lowest 10 Unemployment rates: 
topBSc <- jobLessBSc %>%
  arrange(value)%>%
  select(region, value)%>%
  slice(1:10)

#Find which states have the highest 10Unemployment rates: 
bottomBSc <- jobLessBSc %>%
  arrange(desc(value))%>%
  select(region, value)%>%
  slice(1:10) 
```

### MSc
Apply the same procedure as in BSc
```{r }
#Find   which states have  the lowest 10  Unemployment rates: 
topMSc <- jobLessMSc %>%
  arrange(value)%>%
  select(region, value)%>%
  slice(1:10)

#Find   which states have  the highest 10  Unemployment rates: 
bottomMSc <- jobLessMSc %>%
  arrange(desc(value))%>%
  select(region, value)%>%
  slice(1:10) 
```

###PhD
Apply the same procedure as in BSc

```{r}
#Find   which states have  the lowest 10  Unemployment rates: 
topPhD <- jobLessPhD %>%
  arrange(value)%>%
  select(region, value)%>%
  slice(1:10)

#Find   which states have  the highest 10  Unemployment rates: 
bottomPhD <- jobLessPhD %>%
  arrange(desc(value))%>%
  select(region, value)%>%
  slice(1:10) 
```

## Common States

Now let us see if there are common states between the top 10 and the bottom 10 of each degree group

#### States  with lowest Unemployment Rate
```{r}
Reduce(intersect, list(topPhD$region, topMSc$region, topBSc$region))
```

####States  with lowest Unemployment Rate

```{r}
Reduce(intersect, list(bottomPhD$region, bottomMSc$region, bottomBSc$region))
```

Interestingly, there are a common states repeated in the three degree levels. The states  of "Oregon", "Massachusetts", "California" has the hieghest unemployment rate in all degree levels (B.Sc, MSc, and PhD) whereas "montana", "oklahoma"  have the lowest unemployment rate in all degree levels.  

It is worth investigaing why!!
  
Now, those who were lucky enough, pursued higher level of education, and secured jobs, do they really get paid higher?

#What about their income?
Last question: do PhD degrees earn more than the rest of the guys? In this part, we exclude those who earns less than $ $1000 $
  
Because of the large number of data, we conduct the analysis on a sample. To make it more generalizable, for each degree level we randomly draw $5000$ samples (subset) of $1000$ observations each and compute  some statistics (`min()`, `max()`, `median()`, and `IQR()`) of the income in that sample.

```{r}
#random sample  for plotting
aboveThousand <- ds %>%
  filter(PINCP>1000)%>%
  group_by(SCHL) 
freq <- 5000 #How many subsets are we creating
allStat <- NULL
for(i in 1:freq){
  tempSample <-  sample_n(aboveThousand,1000)
  sampleStat <- summarise(tempSample, MinIncome=min(PINCP), MaxIncome=max(PINCP),
                          MedianIncome=median(PINCP), IncomeRange=IQR(PINCP))  
  allStat <- rbind(allStat, sampleStat)
}
ranSamples <- allStat %>% 
  arrange(SCHL) 
```

Then average over these  statistics to get the  mean of each statistic: 
```{r}
SummaryStat <- ranSamples %>%
  group_by(SCHL) %>%
  select(MinIncome,  MaxIncome,  MedianIncome,  IncomeRange)%>%
  lapply(mean, na.rm = TRUE)
ranSamples <- left_join(ranSamples , degreCodes, by.x=c("SCHL"))   
```


So the box plot  below compares the mean of the medians of the $5000$ subsets for each degree B.Sc, MSc, and PhD:
```{r, echo=FALSE}
Degrees <- factor(ranSamples$DegLevel, levels = unique(ranSamples$DegLevel))
ggplot(ranSamples, aes(x=Degrees, y=MedianIncome, fill=Degrees ) ) +  
  geom_boxplot(notch = FALSE, outlier.colour="#CC6600") +
  scale_fill_manual(name = "", values = c("#00BFFF", "#66FF00", "#CC0033")) +
  theme(panel.background = element_rect(fill = 'white' )) +
  ggtitle("Comparing Income of Degrees Holders")  
```


Also show the distribution of the medians in each sample in each group using the density plot:
  
```{r, echo=FALSE}
#Extract
dsMedians <- ranSamples%>%
  select(MedianIncome, SCHL)
BSc <- filter(dsMedians,SCHL==21)%>%
  log10()
MSc <- filter(dsMedians,SCHL==22)%>%
  log10()
PhD <- filter(dsMedians,SCHL==24)%>%
  log10()
#Plots
ggplot(BSc, aes(x=MedianIncome,color="BSc")) + geom_density( fill= "#00BFFF55") +
  ylab("Density") + xlab("Income") +  ggtitle("Income Dist: BSc, MSc, PhD") +   
  geom_density(data=MSc, aes(color="MSc"),    fill= "#66FF0055") +
  geom_density(data=PhD, aes(color="PhD"),    fill= "#CC003355") +
  theme(panel.background = element_rect(fill = 'white' )) +
  scale_colour_manual(values=c(BSc="#00BFFF", MSc="#66FF00", PhD ="#CC0033"), name="") 
```

#Conclusions
Yes, it is worth pursuing your education and worth doing a PhD as you will end up being paid higher than other degree levels. Actually, there are so many of B.sc and MSc guys than PhDs, so try get out of the crowd and do a PhD if you can. 

However, try not to do it in "Oregon", "Massachusetts", or "California" as these 'enjoy' the highest unemployment rates in all degree levels not just PhD. Be smarter and look for a job in other states like  "Montana"  "Oklahoma" or others shown on the maps and listed in the top 10 and bottom 10 analysis. 

Actually you can still get away with a B.Sc in these states but you will sacrify higher income!
  
#Next Satge
What are the reasons behind the low and high unemployment rates in some specific states?[Script](https://www.kaggle.com/owise83/2013-american-community-survey/i-did-a-phd-where-to-look-for-a-job)

