---
title: "Stem Completion"
author: "Arpita Shah and Tian Zheng"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

HappyDB is a corpus of 100,000 crowd-sourced happy moments via Amazon's Mechanical Turk. You can read more about it on https://arxiv.org/abs/1801.07746

In this R notebook, we process the raw textual data for our data analysis.

### Step 0 - Load all the required libraries

From the packages' descriptions:

+ `tm` is a framework for text mining applications within R;
+ `tidyverse` is an opinionated collection of R packages designed for data science. All packages share an underlying design philosophy, grammar, and data structures;
+ `tidytext` allows text mining using 'dplyr', 'ggplot2', and other tidy tools;
+ `DT` provides an R interface to the JavaScript library DataTables.

```{r load libraries, warning=FALSE, message=FALSE}
library(tm)
library(tidytext)
library(tidyverse)
library(DT)
```

### Step 1 - Load the data to be cleaned and processed

```{r read data, warning=FALSE, message=FALSE}
urlfile<-'https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/cleaned_hm.csv'
hm_data <- read_csv(urlfile)
```

### Step 2 - Preliminary cleaning of text

We clean the text by converting all the letters to the lower case, and removing punctuation, numbers, empty words and extra white space.

```{r text processing in tm}
corpus <- VCorpus(VectorSource(hm_data$cleaned_hm))%>%
  tm_map(content_transformer(tolower))%>%
  tm_map(removePunctuation)%>%
  tm_map(removeNumbers)%>%
  tm_map(removeWords, character(0))%>%
  tm_map(stripWhitespace)
```

### Step 3 - Stemming words and converting tm object to tidy object

Stemming reduces a word to its word *stem*. We stem the words here and then convert the "tm" object to a "tidy" object for much faster processing.

```{r stemming}
stemmed <- tm_map(corpus, stemDocument) %>%
  tidy() %>%
  select(text)
```

### Step 4 - Creating tidy format of the dictionary to be used for completing stems

We also need a dictionary to look up the words corresponding to the stems.

```{r tidy dictionary}
dict <- tidy(corpus) %>%
  select(text) %>%
  unnest_tokens(dictionary, text)
```

### Step 5 - Removing stopwords that don't hold any significant information for our data set

We remove stopwords provided by the "tidytext" package and also add custom stopwords in context of our data.

```{r stopwords}
data("stop_words")

word <- c("happy","ago","yesterday","lot","today","months","month",
                 "happier","happiest","last","week","past")

stop_words <- stop_words %>%
  bind_rows(mutate(tibble(word), lexicon = "updated"))
```

### Step 6 - Combining stems and dictionary into the same tibble

Here we combine the stems and the dictionary into the same "tidy" object.

```{r tidy stems with dictionary}
completed <- stemmed %>%
  mutate(id = row_number()) %>%
  unnest_tokens(stems, text) %>%
  bind_cols(dict) %>%
  anti_join(stop_words, by = c("dictionary" = "word"))
```

### Step 7 - Stem completion

Lastly, we complete the stems by picking the corresponding word with the highest frequency.

```{r stem completion, warning=FALSE, message=FALSE}
completed <- completed %>%
  group_by(stems) %>%
  count(dictionary) %>%
  mutate(word = dictionary[which.max(n)]) %>%
  ungroup() %>%
  select(stems, word) %>%
  distinct() %>%
  right_join(completed) %>%
  select(-stems)
```

### Step 8 - Pasting stem completed individual words into their respective happy moments

We want our processed words to resemble the structure of the original happy moments. So we paste the words together to form happy moments.

```{r reverse unnest}
completed <- completed %>%
  group_by(id) %>%
  summarise(text = str_c(word, collapse = " ")) %>%
  ungroup()
```

### Step 9 - Keeping a track of the happy moments with their own ID

```{r cleaned hm_data, warning=FALSE, message=FALSE}
hm_data <- hm_data %>%
  mutate(id = row_number()) %>%
  inner_join(completed)

datatable(hm_data)
```

### Exporting the processed text data into a CSV file

```{r export data}
write_csv(hm_data, "../output/processed_moments.csv")
```

The final processed data is ready to be used for any kind of analysis.