---
title: "Evaluation for Project 3"
author: "Yuting Ma"
date: "March 9, 2016"
output: html_document
---

### Submission Structure
The submission folder must contain the following objects

*  `./lib`
    +  `train.R`
    +  `test.R`
*  `./output`
    +  `feature_eval.RData`

### Load constructed features for the entire evaluation image set
* Note that the constructed features for evaluation must be saved as a 2D array (matrix) format
* Each row of the feature matrix **MUST** match the given file name indices. 
    + Sample filename-index file will look like
```{r, eval=FALSE}
  ind               name
1   1   Abyssinian_1.jpg
2   2  Abyssinian_10.jpg
3   3 Abyssinian_100.jpg
4   4 Abyssinian_101.jpg
5   5 Abyssinian_102.jpg
6   6 Abyssinian_103.jpg
```
* The file `feature_eval.RData` should contain the object `feature_eval`, which is a matrix of size $n \times p$ with each row corresponds to each raw image.
```{r, eval=FALSE}
load("./output/feature_eval.RData") 
```


### Load class labels for evaluation image set
* The file  `label_eval.RData` contains an object `label_eval`, which is a vector of length n (2000) with 0/1 entries.
```{r, eval=FALSE}
load("label_eval.RData") 
```

### Cross Validation
* `train.R`
    + Input: 
        - `dat_train`: constructed features for training data
        - `label_train`: class labels for training data
    + Output: model specification in any format that can be read in `test.R`. The output should contain model specifications for both the baseline model and the advanced model. 
* `test.R`
    + Input: 
        - `fit_train`: model specification resulted from the training process, can be any format
        - `dat_test`: construted features for testing data
    + Output: a list of two vectors of class label prediction in 0/1 (0=dog,1=cat) based on the basline model and the advanced model respectively. 
        - `$baseline`: class label prediction of baseline model
        - `$adv`: class label prediction of advanced model 
* Required packages need to be properly installed in `train.R` and `test.R`
    + The packages should be compatible with `R version 3.2.3 (2015-12-10) -- "Wooden Christmas-Tree"`
    + If other library, such as Python packages, is required, please let us know in advance.
* Randomization: All group will be evaluated on the same partitions of data

```{r, eval=FALSE}
source("./lib/train.R")
source("./lib/test.R")

n <- 2000
n_rep <- 20
K <- 5
ind_cat <- which(eval_label == 1) # 1000 cats
ind_dog <- which(eval_label == 0) # 1000 dogs
n_cat_fold <- n_dog_fold <- 200

CV_err_baseline <- rep(0, n_rep)
CV_err_adv <- rep(0, n_rep)
CV_fit_baseline <- array(dim=c(n, n_rep))
CV_fit_adv <- array(dim=c(n, n_rep))
train_time <- array(dim=c(K, n_rep))

for(r in 1:n_rep){
  set.seed(309+r)
  assign_cat <- sample(rep(1:K, times=n_cat_fold))
  set.seed(1310+r)
  assign_dog <- sample(rep(1:K, times=n_dog_fold))
  
  CV_index <- rep(NA, n)
  CV_index[ind_cat] <- assign_cat
  CV_index[ind_dog] <- assign_dog
  
  for(c in 1:K){
    cat("fold= ", c, "\n")
    ind_test <- which(CV_index == c)
    dat_train <- feature_eval[-ind_test,]
    label_train <- label_eval[-ind_test]
    dat_test <- feature_eval[ind_test,]
    label_test <- label_eval[ind_test]
    train_time[c,r] <- system.time(mod_train <- train(dat_train, label_train))[1]
    pred_test <- test(mod_train, dat_test)
    CV_fit_baseline[ind_test, r] <- pred_test$baseline
    CV_fit_adv[ind_test, r] <- pred_test$adv
  }
  cv_err_baseline[r] <- mean(CV_fit_baseline[,r] != label_eval)
  cv_err_adv[r] <- mean(CV_fit_adv[,r] != label_eval)
  
}

save(CV_fit_baseline, CV_fit_adv,  cv_err_baseline, cv_err_adv, train_time, file="CV_result.RData")
```

### Evaluation
* CV error will be used to evalute the performance
```{r, eval=FALSE}
mean(CV_fit != label_eval)
```
* Stability is evaluated using the variance of CV error among different data partitions.
```{r, eval=FALSE}
sd(cv_err_baseline)
sd(cv_err_adv)
```
* Average training time will be used to evaluate computational efficiency
```{r, eval=FALSE}
mean(train_time)
```