---
title: "Summary of Project 3"
author: "Chengliang Tang"
date: "April 21, 2017"
output:
  html_document: default
  pdf_document: default
---

## Feature extraction, storage, running time (cost)

### Submission Time
```{r, echo=FALSE}
# run Results.R first
submitTime <- c(0, 16, 43, 27, 450, 84, 0, 1, 8, 231, 400, 0, 127, 37)
submitTime_label <- c("In Time", "3:31PM", "3:58PM", "3:42PM", "Three days later", "4:39PM", "In Time", "3:16PM", "3:23PM", "7:06PM", "Two days later", "In time", "5:22PM", "3:52PM")

bar_time <- barplot(submitTime, main="Submission Time: Minutues from 3:15PM",
        xlab="Team", ylab="Minutes", ylim=c(0, 650))
text(bar_time, submitTime+30, submitTime_label, cex=0.6)
axis(1, bar_time, labels=as.character(1:14))
```

### Dimensions of Extracted Features
#### Advanced Model
Advanced Features: GIST(1), resized SIFT(2, 10, 11, 13), CNN(3), LBP(4, 6), HoG(5, 7, 8, 9), grayscale(12), raw images(14)
```{r, echo=FALSE}
featureDim_bl <- c(512, 5000, 350, 59, 200, 830, 54, 5448, 57, 128, 383, 2131, 300, 2500)
log_featureDim_bl <- log(featureDim_bl)
bar_dim_bl <- barplot(log_featureDim_bl, main="Extracted Advanced Feature Dimensions",
                       xlab="Team", ylab="log(p)", ylim=c(0, 12))
text(bar_dim_bl, log_featureDim_bl+0.5, as.character(featureDim_bl), cex=0.8)
axis(1, bar_time, labels=as.character(1:14))
```

### Running Time
Advanced models: SVM(5, 7, 10, 11, 13), xgboost(1, 2, 6), majority vote(4), random forest(9, 12), model ensemble(3, 8), DNN(14)
```{r, echo=FALSE}
# run Results.R first
RunningTime <- c(60, 57, 7, 30, 10, 10, 9, 65, 8, 120, 120, 180, 10, 660)
log_RunningTime <- log(RunningTime)
bar_time <- barplot(log_RunningTime, main="Advanced Model Running Time",
        xlab="Team", ylab="log(t)", ylim=c(0, 10))
text(bar_time, log_RunningTime+0.5, as.character(RunningTime), cex=0.8)
axis(1, bar_time, labels=as.character(1:14))
```

## Performance
### Baseline Prediction Accuracy

```{r, echo=FALSE}
# data saved in Results.R
err_claimed <- c(0.271, 0.2365, 0.2875, 0.275, 0.33, 0.23, 0.3003, 0.235, 0.2743, 0.294, 0.27, 0.238, 0.306, 0.27)
err_adv_claimed <- rep(err_claimed, each=20)
CV_error_baseline <- c(
  0.2525, 0.2225, 0.28, 0.27, 0.2325,
  0.245, 0.2575, 0.275, 0.265, 0.3025,
  0.25, 0.2525, 0.2275, 0.2125, 0.23,
  0.2325, 0.2275, 0.2525, 0.2525, 0.225,
  0.2225, 0.2475, 0.2450, 0.2225, 0.2650,
  0.26, 0.255, 0.32, 0.265, 0.2725,
  0.2625, 0.3075, 0.265, 0.2525, 0.3100,
  0.28, 0.325, 0.2975, 0.2825, 0.3075,
  0.2425, 0.2975, 0.2775, 0.2625, 0.29,
  0.3025, 0.3175, 0.3, 0.27, 0.3025,
  0.2275, 0.2325, 0.2275, 0.2275, 0.235,
  0.21, 0.2025, 0.2075, 0.2075, 0.1975,
  0.2525, 0.29, 0.2675, 0.2475, 0.2825,
  0.2625, 0.2575, 0.27, 0.2325, 0.245
)
# load("label_eval.RData")
# load("pred_untuned.RData")
# ind_fun <- which(is.na(label_eval))
err_untuned <- c(0.3115, 0.3055, 0.305, 0.302, 0.511, 0.3845, 0.296, 0.3125, 0.301, 0.323, 0.3245, 0.305, 0.3145, 0.5155)
err_adv_untuned <- rep(err_untuned  , each=20)

type_names <- c("claimed", "untuned", "re-trained")
# team_names <- paste0("Team ", 1:12)
team_names <- 1:14
# load("output_proj3.RData")
err_adv_all <- data.frame(Team=rep(rep(team_names, each=20), times=3), 
  					  Type=rep(type_names, each=280),
						  Error= c(err_adv_claimed, err_adv_untuned, rep(CV_error_baseline, each = 4))) #as.vector(t(output$err_adv_retrained))))

err_adv_all$Type <- factor(err_adv_all$Type, levels= type_names)
err_adv_all$Team <- factor(err_adv_all$Team, levels= team_names)


err_adv_all$Error <- err_adv_all$Error*100

type_names <- c("claimed", "untuned", "re-trained")
team_names <- paste0("Team ", 1:14)

library(ggplot2)
(ggplot(err_adv_all, aes(y = Error, x = Team, fill = Type, colour = Type)) 
+ geom_boxplot(width=0.5,outlier.colour = NULL)
#+ scale_alpha_continuous(guide=FALSE, range=c(0.01,0.99))
+theme(axis.line = element_line(colour = "black"),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_rect(colour = "black", fill=NA),
      axis.text=element_text(size=12),
      axis.title=element_text(size=12),
      legend.text=element_text(size=12),
      legend.title=element_text(size=12, face="bold"),
      legend.position="bottom",
      strip.text.y = element_text(size = 13, face="bold"),
      panel.background = element_blank())
+ labs(title="Baseline Model CV Error (%)", x="Team", y="Error Rate")
+ scale_colour_brewer(palette = "Dark2", guide = FALSE)
+ scale_fill_brewer(palette = "Pastel2", labels=type_names, guide = guide_legend(title = "Type"))
+ geom_vline(xintercept = seq(1.5, 13.5, 1), linetype = "longdash", colour="lightgrey")) 

```

### Advanced Prediction Accuracy
Advanced Features: GIST(1), resized SIFT(2, 10, 11, 13), CNN(3), LBP(4, 6), HoG(5, 7, 8, 9), grayscale(12), raw images(14)

Advanced models: SVM(5, 7, 10, 11, 13), xgboost(1, 2, 6), majority vote(4), random forest(9, 12), model ensemble(3, 8), DNN(14)

```{r, echo=FALSE}
err_claimed <- c(0.142, 0.189, 0.0475, 0.1312, 0.12, 0.10, 0.122, 0.107, 0.07, 0.188, 0.09, 0.006, 0.1975, 0.19)
err_adv_claimed <- rep(err_claimed, each=20)
CV_error_adv <- c(
  0.135, 0.1425, 0.19, 0.1325, 0.135,
  0.1480, 0.1470, 0.1510, 0.1355, 0.1510,
  0.0175, 0.04, 0.03, 0.015, 0.0275,
  0.04, 0.0525, 0.0775, 0.055, 0.0575,
  0.1675, 0.1250, 0.1775, 0.1950, 0.1550,
  0.0925, 0.0775, 0.09, 0.095, 0.095,
  0.075, 0.0775, 0.06, 0.0775, 0.08,
  0.0625, 0.065, 0.065, 0.0675, 0.05,
  0.0375, 0.02, 0.03, 0.05, 0.0325,
  0.175, 0.17, 0.205, 0.2025, 0.195,
  0.25, 0.245, 0.5175, 0.2575, 0.2725,
  0, 0.005, 0, 0.005, 0,
  0.1775, 0.185, 0.21, 0.21, 0.2,
  0.26, 0.135, 0.15, 0.1425, 0.14
)
#load("label_eval.RData")
#load("pred_untuned.RData")
# ind_fun <- which(is.na(label_eval))
err_untuned <- c(0.1695, 0.3415, 0.041, 0.1275, 0.379, 0.2905, 0.1495, 0.197, 0.079, 0.27, 0.341, 0.0655, 0.2335, 0.183)
err_adv_untuned <- rep(err_untuned  , each=20)

type_names <- c("claimed", "untuned", "re-trained")
# team_names <- paste0("Team ", 1:12)
team_names <- 1:14
# load("output_proj3.RData")
err_adv_all <- data.frame(Team=rep(rep(team_names, each=20), times=3), 
  					  Type=rep(type_names, each=280),
						  Error= c(err_adv_claimed, err_adv_untuned, rep(CV_error_adv, each = 4))) #as.vector(t(output$err_adv_retrained))))

err_adv_all$Type <- factor(err_adv_all$Type, levels= type_names)
err_adv_all$Team <- factor(err_adv_all$Team, levels= team_names)


err_adv_all$Error <- err_adv_all$Error*100

type_names <- c("claimed", "untuned", "re-trained")
team_names <- paste0("Team ", 1:14)

library(ggplot2)
(ggplot(err_adv_all, aes(y = Error, x = Team, fill = Type, colour = Type)) 
+ geom_boxplot(width=0.5,outlier.colour = NULL)
#+ scale_alpha_continuous(guide=FALSE, range=c(0.01,0.99))
+theme(axis.line = element_line(colour = "black"),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_rect(colour = "black", fill=NA),
      axis.text=element_text(size=12),
      axis.title=element_text(size=12),
      legend.text=element_text(size=12),
      legend.title=element_text(size=12, face="bold"),
      legend.position="bottom",
      strip.text.y = element_text(size = 13, face="bold"),
      panel.background = element_blank())
+ labs(title="Advanced Model CV Error (%)", x="Team", y="Error Rate")
+ scale_colour_brewer(palette = "Dark2", guide = FALSE)
+ scale_fill_brewer(palette = "Pastel2", labels=type_names, guide = guide_legend(title = "Type"))
+ geom_vline(xintercept = seq(1.5, 13.5, 1), linetype = "longdash", colour="lightgrey")) 

```



  
  
  
  
  
  
  
  
  
  
  
 

